\documentclass[../main.tex]{subfiles}
 
\begin{document}

\section{Welcome to Anaheim}

You wake up early to take the bus from Boulder to Denver International Airport. During the flight, you finish reading \textit{How to Get Filthy Rich in Rising Asia} by Mohsin Hamid. You find the second-person conceit refreshing and decide you might as well give that a try when you write about your experiences at SIGGRAPH. You secretly wonder how many people at the airport or on your plane whole-heartedly believe or, like you, at least want to believe the conspiracy theories surrouding Denver International Airport. You hear one lady seated near you in terminal make a reference to this and you smile. There \textit{is} something up with DIA. You've seen the strange artwork and read about the Masonic symbols. You're happy your home airport is this interesting, because you hope to fly out of it a few times this year.

Arriving at John Wayne Airport in Orange County, you are struck by the awful heat wave they are currently experiencing and your excitement for your Anaheim trip falters as you head through Friday midday traffic in the back seat of your Uber driver's cluttered Scion xB. After 30 minutes of motoring, you retrieve a key from the lockbox at the big empty house where your Airbnb host lives. It's Friday. On Saturday you must report for a day of SV orientation before SIGGRAPH kicks off the following day. You make it out on foot through the seedy strip of South Beach Boulevard to grab a few groceries. You feel fairly close to experiencing heat stroke for the first time as you jog to the nearest CVS to stash a week's worth of snacks in your kitchen. You'll be commuting 15 minutes each day from your host's home to the convention center. Meals will \sout{occasionally} often consist of restaurants and daily over-priced bento boxes for breakfast (and lunch) from a Hilton Starbucks next to the convention center.

You decide not to waste the Uber fare on exploring the Conventon Center, deciding instead to hang out sweating in your bedroom where it never falls below 85 degrees, despite the A/C set on full blast. You wonder if this was one of those big cardboard homes built just before the 2008 financial crisis. Everything about it seems cheep but it is surrounded by a nice park and your particular street is decorated with 5 Series models and the like. You download \textit{Pit Bull: The Battle over an American Icon} by Bronwen Dickey so that you can follow through with a recent book recommendation from a family friend you met in Boulder a few weeks prior. It was your intention to read at least one book all the way through during your Anaheim stay. You manage to fall asleep in the aweful heat.
 
\end{document}