\documentclass[../main.tex]{subfiles}
 
\begin{document}

\section{Welcome to Anaheim}

You wake up early take the bus from Boulder to Denver International Aiport. During the flight, you finish reading \textit{How to Get Filthy Rich in Rising Asia} by Mohsin Hamid. You find the second-person conceit refreshing and decide you might as well give that a try when you write about your experiences at SIGGRAPH.

Arriving at John Wayne Airport in Orange County, you are struck by the aweful heat wave they are currently experiencing and your excitement for your Anaheim trip faulters as you head through Friday midday traffic in the back seat of your Uber driver's Scion xB. After 30 minutes, you retrieve a key from the lockbox at the big empty house where your Airbnb host lives. It's Friday. On Saturday you must report for a day of SV orientation before SIGGRAPH begins the following day. You make it out on foot through the seedy strip of South Beach Boulevard to grab a few groceries. You nearly heat stroke as you jog to the nearest CVS to stash a week's worth of snacks in your kitchen. You'll be commuting 15 minutes each day from your host's home to the convention center. Meals will consist of occasional restaurants and daily over-priced bento boxes from a Hilton Starbucks next to the convention center.

You decide not to waste the Uber fare on exploring the conventon center, deciding instead to hang out sweating in your bedroom where it never falls below 85 degrees, despite the A/C efforts. You download \textit{Pit Bull} by Bronwen Dicky so that you can follow through with a recent book recommendation from a family friend you met in Boulder. It was your intention to read at least one book through during your Anaheim stay: you enjoyed racing through Hamid's novel the previous night and during your flight. Somehow, you manage to fall asleep in the aweful heat.
 
\end{document}