\documentclass[../main.tex]{subfiles}
 
\begin{document}

\section{Orientation}

On Saturday you wake up happy to have managed to snatch 8 hours of sleep before your first day. You tend to experience sleep anxiety so you hope to keep up this good momentum throughout the week. You pack your slim messenger bag and are shorty greeted by an Uber driver stopped in the middle of the street in front of your house. It's early, and there was literally one car available at 7:30am near your neighborhood.

After a pricey but filling breakfast at Park 55 just down the street from the Anaheim Convention center, you make your way to the second floor's makeshift Student Volunteer office, where you plop yourself down on one of the many beanbag chairs in the back of the room and continue working through \textit{Pit Bull} to pass the few hours that remain before noon check-in. You are quite early: many SV's will be getting off the plane and booking it to the convention center for check-in.

Before long, you are recruited to help out on the main showroom, guided by a Team Leader wearing a purple Dreamworks shirt and holding a clipboard and a walkie talkie. For the next two hours, you load a couple thousand packets of papers and other goodies into tote bags which will be handed out to attendees. You're more than happy to keep your hands busy, as this is a day of sitting and waiting. You chat with other students, some still in school studying animation or computer science, others established at companies like MPC, working on rendering pipeline tools. It is at this point you sense the tension that naturally exists between the students rearing to get into industry and the folks who are fortunate to already have jobs. You consider yourself among the fortunate, and hope to never come across as standoffish as the one girl who's job was admittedly about as good as one could hope for in this line of work.

During check-in you fall in with a group that develops out of the people who happen to be standing in line near you---a line of a few hundred student volunteers that will take nearly 2 hours to deliver you to a table where you are handed a conference badge, two orange Dreamworks Student Volunteer shirts, and a whiteboard on which you write your name before having your mugshot taken. Showreels and clever business cards come out and you are impressed by this work. Afterall, you are not an artist and cannot help but be impressed by both the incredible talent and the daunting challenge of actually entering the industry your fellow student volunteers aspire towards. Again, you feel fortunate for your line of work. Conversations quickly turn to the current suite of tools each student is trying to learn and efforts to expand portfolios in the months following graduation. All in the hopes of making a company like Pixar or perhaps Naughty Dog take an interest in them.

Between check-in and orientation in the late afternoon, you are free to kill some time. You join several of the people you were talking to in line and grab mediterranean food.

\end{document}